\begin{thebibliography}{}

%%%%%%%%%%%% Week 1
\bibitem{epfl}
	École Polytechnique Fédérale de Lausanne,
	\emph{EE-559 - Deep Learning}.

\bibitem{places365}
	B. Zhou, A. Lapedriza, A. Khosla, A. Oliva, A. Torralba,
	\emph{Places: A 10 million Image Database for Scene Recognition},
    IEEE Transactions on Pattern Analysis and Machine Intelligence, 2017.

\bibitem{caffe}
	Jia, Yangqing and Shelhamer, Evan and Donahue, Jeff and Karayev, Sergey and Long, Jonathan and Girshick, Ross and Guadarrama, Sergio and Darrell, Trevor,
	\emph{Caffe: Convolutional Architecture for Fast Feature Embedding},
    arXiv:1408.5093, 2014.

\bibitem{pytorch}
    Adam Paszke, Sam Gross, Soumith Chintala, Gregory Chanan,
    \emph{PyTorch}.

\bibitem{alexnet}
	Alex Krizhevsky, Ilya Sutskever, Geoffrey E. Hinton,
    \emph{ImageNet Classification with Deep Convolutional Neural Networks}.

\bibitem{resnet}
	Kaiming He, Xiangyu Zhang, Shaoqing Ren, Jian Sun,
	\emph{Deep Residual Learning for Image Recognition},
    arXiv:1512.03385, 2015.

\bibitem{densenet}
	Gao Huang, Zhuang Liu, Laurens van der Maaten, Kilian Q. Weinberger,
    \emph{Densely Connected Convolutional Networks},
    arXiv:1608.06993, 2016.

\bibitem{cam}
	Bolei Zhou, Aditya Khosla, Agata Lapedriza, Aude Oliva, Antonio Torralba,
	\emph{Learning Deep Features for Discriminative Localization},
	arXiv:1512.04150, 2015.

\bibitem{googlenet}
	Christian Szegedy, Wei Liu, Yangqing Jia, Pierre Sermanet, Dragomir Anguelov, Dumitru Erhan, Vincent Vanhoucke, Andrew Rabinovich, Scott Reed,
	\emph{Going Deeper with Convolutions},
	arXiv:1409.4842, 2014.

%%%%%%%%%%%% Week 2

\bibitem{miniproject1}
	École Polytechnique Fédérale de Lausanne
	\emph{EE-559 - Deep Learning},
	\emph{Mini-project 1: Prediction of finger movements from EEG recordings}.

\bibitem{vggnet}
	Karen Simonyan, Andrew Zisserman,
    \emph{Very Deep Convolutional Networks for Large-Scale Image Recognition},
    arXiv:1409.1556, 2014.

\bibitem{yolo}
    Joseph Redmon, Santosh Divvala, Ross Girshick, Ali Farhadi,
    \emph{You Only Look Once: Unified, Real-Time Object Detection}.

\bibitem{semanticseg}
	Ross Girshick, Jeff Donahue, Trevor Darrell and Jitendra Malik,
    \emph{Rich feature hierarchies for accurate object detection and semantic segmentation},
	arXiv:1311.2524, 2013.

\bibitem{eegrecord}
	G. C. Benjamin Blankertz and K.-R. R. Muller,
    \emph{Towards brain computer interfacing},
	\emph{Neural Information Processing Systems (NIPS)},
	2002.

%%%%%%%%%%%% Week 3

\bibitem{dlib}
	Davis E. King,
    \emph{DLib}.


%%%%%%%%%%% Week 4

\bibitem{cs231n}
	Stanford University,
	CS231n - Convolutional Neural Networks for Visual Recognition.

\bibitem{cifar}
    Alex Krizhevsky, Vinod Nair, and Geoffrey Hinton.
	\emph{CIFAR-10 dataset}.



\bibitem{batchnorm}
    Sergey Ioffe, Christian Szegedy
    \emph{Batch Normalization: Accelerating Deep Network Training by Reducing Internal Covariate Shift}.

%%%%%%

\bibitem{cvpr17}
	Conference on Computer Vision and Pattern Recognition 2017.

\bibitem{iccv17}
	International Conference on Computer Vision 2017,
    \emph{2017.thecvf.com}.

\bibitem{cvpr18}
	Conference on Computer Vision and Pattern Recognition 2018.

\bibitem{adda}
    Eric Tzeng, Judy Hoffman, Kate Saenko, Trevor Darrell,
    \emph{Adversarial Discriminative Domain Adaptation},
    arXiv:1702.05464, 2017.

\bibitem{rozantsev}
    Artem Rozantsev, Mathieu Salzmann, Pascal Fua,
    \emph{Beyond Sharing Weights for Deep Domain Adaptation},
    arXiv:1603.06432, 2016.

\bibitem{cgan}
    Mehdi Mirza, Simon Osindero,
    \emph{Conditional Generative Adversarial Nets},
    arXiv:1411.1784 2014.

\bibitem{stackgan}
    Han Zhang, Tao Xu, Hongsheng Li, Shaoting Zhang, Xiaogang Wang, Xiaolei Huang, Dimitris Metaxas,
    \emph{Text to Photo-realistic Image Synthesis with Stacked Generative Adversarial Networks},
    arXiv:1612.03242, 2016.

\bibitem{stackganv2}
    Han Zhang, Tao Xu, Hongsheng Li, Shaoting Zhang, Xiaogang Wang, Xiaolei Huang, Dimitris Metaxas,
    \emph{StackGAN++: Realistic Image Synthesis with Stacked Generative Adversarial Networks},
    arXiv:1710.10916, 2017.
    

%%%%%%

\bibitem{gan}
    Ian J. Goodfellow, Jean Pouget-Abadie, Mehdi Mirza, Bing Xu, David Warde-Farley, Sherjil Ozair, Aaron Courville, Yoshua Bengio,
    \emph{Generative Adversarial Networks}
    arXiv:1406.2661, 2014.

\bibitem{sagan}
	Han Zhang, Ian Goodfellow, Dimitris Metaxas and Augustus Odena,
	\emph{Self-Attention Generative Adversarial Networks},
	arXiv:1805.08318, 2018.

\bibitem{spectralnorm}
	Takeru Miyato, Toshiki Kataoka, Masanori Koyama and Yuichi Yoshida,
	\emph{Spectral Normalization for Generative Adversarial Networks},
	arXiv:1802.05957, 2018.

\bibitem{pix2pix}
	Phillip Isola, Jun-Yan Zhu, Tinghui Zhou, Alexei A. Efros,
	\emph{Paired Image-to-image translation using Conditional GAN},
	arXiv:1611.07004, 2016.

\bibitem{pix2pixhd}
	Ting-Chun Wang, Ming-Yu Liu, Jun-Yan Zhu, Andrew Tao, Jan Kautz, and Bryan Catanzaro,
	\emph{High-Resolution Image Synthesis and Semantic Manipulation with Conditional GANs},
	CVPR 2018.

\bibitem{cyclegan}
	Jun-Yan Zhu, Taesung Park, Phillip Isola, Alexei A. Efros,
	\emph{Unpaired Image-to-Image Translation using Cycle-Consistent Adversarial Networks},
	ICCV 2017.

\bibitem{bicyclegan}
	Zhu, Jun-Yan and Zhang, Richard and Pathak, Deepak and Darrell, Trevor and Efros, Alexei A and Wang, Oliver and Shechtman, Eli,
	\emph{Toward Multimodal Image-to-Image Translation},
	arXiv:1711.11586, Nov 2017.

\bibitem{a-fast-rcnn}
	Xiaolong Wang, Abhinav Shrivastava, Abhinav Gupta,
	\emph{A-Fast-RCNN: Hard Positive Generation via Adversary for Object Detection},
    CVPR, 2017.

\bibitem{fast-rcnn}
	Ross Girshick,
    \emph{Fast R-CNN},
    arXiv:1504.08083, 2015.

\bibitem{cyclegangithub}
	Jun-Yan Zhu,
	\emph{pytorch-CycleGAN-and-pix2pix}.

\bibitem{styletransfergithub}
	Cameron Smith,
	\emph{neural-style-tf}.

\bibitem{styletransfer}
	Leon A. Gatys, Alexander S. Ecker, Matthias Bethge,
    \emph{Image Style Transfer Using Convolutional Neural Networks}.

\bibitem{styletransfervideo}
	Manuel Ruder, Alexey Dosovitskiy, Thomas Broxn,
    \emph{Artistic style transfer for videos},
    arXiv:1604.08610, 2016.

\bibitem{preservingcolor}
	Leon A. Gatys, Matthias Bethge, Aaron Hertzmann, Eli Shechtman,
    \emph{Preserving Color in Neural Artistic Style Transfer},
    arXiv:1606.05897, 2016.

\bibitem{thestarrynight}
	The Starry Night by Vincent van Gogh,
	1889.

%%%%%%%%%% Week 8

\bibitem{mediaeval18}
	Multimedia Evaluation 2018,
    \emph{mediaeval2018}.

\bibitem{medico18}
	Medico: The 2018 Multimedia for Medicine Task.

\bibitem{jpeg}
	Joint Photographic Experts Group.

\bibitem{emotion18}
	The 2018 Emotional Impact of Movies Task,
    \emph{emotionalimpact}.

\bibitem{memo18}
	The 2018 Predicting Media Memorability Task,
	\emph{memorability}.

\bibitem{longtermmem}
	James L McGaugh,
    \emph{Memory-a Century of Consolidation},
	Science 287, 5451 (2000), 248-251.

\bibitem{c3d}
	D. Tran, L. Bourdev, R. Fergus, L. Torresani, and M. Paluri,
    \emph{Learning Spatiotemporal Features with 3D Convolutional Networks},
    ICCV 2015.

\bibitem{ucf101}
	Khurram Soomro, Amir Roshan Zamir and Mubarak Shah,
	\emph{UCF101: A Dataset of 101 Human Action Classes From Videos in The Wild},
	CRCV-TR-12-01,
	November 2012.

\bibitem{hmp}
	ALMEIDA, Jurandy; LEITE, Neucimar J.; TORRES, Ricardo da S,
    \emph{Image Processing (ICIP), 2011 18th IEEE International Conference on}.
    IEEE, 2011. p. 3673-3676.

\bibitem{hog}
	Dalal, N. and B. Triggs,
    \emph{Histograms of Oriented Gradients for Human Detection},
    IEEE Computer Society Conference on Computer Vision and Pattern Recognition, Vol. 1 (June 2005), pp. 886–893.

\bibitem{lbp}
	DC. He and L. Wang (1990),
    \emph{Texture Unit, Texture Spectrum, And Texture Analysis},
    Geoscience and Remote Sensing,
	IEEE Transactions on, vol. 28, pp. 509 - 512.

\bibitem{fc7layer}
	SZEGEDY, Christian et al,
    \emph{Rethinking the inception architecture for computer vision},
    Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition. 2016. p. 2818-2826.

\bibitem{orb}
	Ethan Rublee, Vincent Rabaud, Kurt Konolige, and Gary Bradski,
    \emph{Orb: an efficient alternative to sift or surf},
    In Computer Vision (ICCV), 2011,
	IEEE International Conference on, 2011.

\bibitem{keypoints}
	OpenCV
	\emph{Keypoints and Descriptors tutorial}.

%%%%%%%%%% Week 9

\bibitem{cnnarchitectures}
	Eugenio Culurciello, TowardsDataScience,
	\emph{Neural Network Architectures}.

\bibitem{lstm}
	Sepp Hochreiter; Jürgen Schmidhuber,
	\emph{Long Short-Term Memory},
	Neural Computation.

\bibitem{tensorflow}
	Google’s AI organization,
	\emph{TensorFlow}.


\bibitem{torch}
	Ronan Collobert, Koray Kavukcuoglu, Clement Farabet,
    \emph{Torch}.

\bibitem{word2vec}
	Skymind,
    \emph{From word to embeddings}.

%%%%%%%%%% Week 10
\bibitem{lamem}
	Aditya Khosla, Akhil S. Raju, Antonio Torralba and Aude Oliva,
	\emph{Understanding and Predicting Image Memorability at a Large Scale},
	International Conference on Computer Vision,
	2015.

\bibitem{5videomethods}
	Matt Harvey, Coastline Automation,
	\emph{Five video classification methods implemented in Keras and TensorFlow}.

\bibitem{imagememorable}
	Phillip Isola, Jianxiong Xiao, Antonio Torralba and Aude Oliva,
	\emph{What makes an image memorable?},
	IEEE Conference on Computer Vision and Pattern Recognition,
	2011.

\bibitem{simplefeatures}
	T. Konkle, T. F. Brady, G. A. Alvarez, and A. Oliva,
	\emph{Conceptual distinctiveness supports detailed visual long-term memory for realworld objects},
	JEP:G, 2010.

\bibitem{labelme}
	B. C. Russell, A. Torralba, K. P. Murphy, and W. T. Freeman,
	\emph{LabelMe: a database and web-based tool for image annotation},
	IJCV, 2008.

%%%%%%%%%% Week 12
\bibitem{amnet}
	Jiri Fajtl, Vasileios Argyriou, Dorothy Monekosso, Paolo Remagnino,
	\emph{AMNet: Memorability Estimation with Attention},
	arXiv:1804.03115, 2018.

\bibitem{visualatt}
	Kelvin Xu, Jimmy Ba, Ryan Kiros, Kyunghyun Cho, Aaron Courville, Ruslan Salakhutdinov, Richard Zemel, Yoshua Bengio,
	\emph{Show, Attend and Tell: Neural Image Caption Generation with Visual Attention},
	arXiv:1502.03044, 2015.

\bibitem{adam}
	Diederik P. Kingma, Jimmy Ba,
	\emph{Adam: A Method for Stochastic Optimi-zation},
	arXiv:1412.6980, 2014.

\end{thebibliography}